---
title: "logger data"
author: "jillashey"
date: '2022-07-11'
output: html_document
---

This script plots Hobo temperature and light data from an adult acute thermal stress experiment at HIMB 2022. 

## Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(tidyverse)
library(emmeans)
library(gridExtra)
```

## Read data in 
```{r}
## Ambient
# Ambient Header
amb_header <- read.csv("../data/temperature/20220719/Amb_Header_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
amb_header$Treatment <- "Ambient"
amb_header$Tank <- "Ambient-Header"

# Amb Tank 1 A
amb_tank1_A <- read.csv("../data/temperature/20220719/Amb1_Tank_A_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
amb_tank1_A$Treatment <- "Ambient"
amb_tank1_A$Tank <- "Ambient1-Tank-A"

# Amb Tank 1 B
amb_tank1_B <- read.csv("../data/temperature/20220719/Amb1_Tank_B_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
amb_tank1_B$Treatment <- "Ambient"
amb_tank1_B$Tank <- "Ambient1-Tank-B"

# Amb Tank 2 A
amb_tank2_A <- read.csv("../data/temperature/20220719/Amb2_Tank_A_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
amb_tank2_A$Treatment <- "Ambient"
amb_tank2_A$Tank <- "Ambient2-Tank-A"

# Amb Tank 2 B
amb_tank2_B <- read.csv("../data/temperature/20220719/Amb2_Tank_B_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
amb_tank2_B$Treatment <- "Ambient"
amb_tank2_B$Tank <- "Ambient2-Tank-B"



## High
# High Header
high_header <- read.csv("../data/temperature/20220719/High_Header_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
high_header$Treatment <- "High"
high_header$Tank <- "High-Header"

# High Tank 1 A
high_tank1_A <- read.csv("../data/temperature/20220719/High1_Tank_A_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
high_tank1_A$Treatment <- "High"
high_tank1_A$Tank <- "High1-Tank-A"

# High Tank 1 B
high_tank1_B <- read.csv("../data/temperature/20220719/High1_Tank_B_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
high_tank1_B$Treatment <- "High"
high_tank1_B$Tank <- "High1-Tank-B"

# High Tank 2 A
high_tank2_A <- read.csv("../data/temperature/20220719/High2_Tank_A_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
high_tank2_A$Treatment <- "High"
high_tank2_A$Tank <- "High2-Tank-A"

# High Tank 2 B
high_tank2_B <- read.csv("../data/temperature/20220719/High2_Tank_B_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
high_tank2_B$Treatment <- "High"
high_tank2_B$Tank <- "High2-Tank-B"
```

## Bind dataframes together and parse data & time
```{r}
data <- rbind(amb_header, amb_tank1_A, amb_tank1_B, amb_tank2_A, amb_tank2_B,
                high_header, high_tank1_A, high_tank1_B, high_tank2_A, high_tank2_B)

colnames(data) <- c("Date.Time", "Temp", "Light", "Treatment", "Tank")
data$Date.Time <- parse_date_time(data$Date.Time, "mdyHMS", tz = "HST")
```

## Subset data after 7/8/22 - when temperature ramp began
```{r}
filt_data <- data %>% filter(Date.Time > "2022-07-08 12:00:00")
```

Plot temperature data
```{r}
temp <- filt_data %>% ggplot(aes(x=Date.Time, y=Temp)) +
  geom_line(aes(color = Tank), size = 1) +
  ylab("Temperature °C") + 
  #geom_vline(xintercept = as.POSIXct(as.Date(c("2022-07-05 18:00:00")))) +
  #geom_vline(xintercept = as.POSIXct(as.Date(c("2022-07-08 18:00:00")))) +
  scale_color_manual(values=c("darkblue", "lightblue", "lightblue", "lightblue", "lightblue", "darkred", "pink", "pink", "pink", "pink"))
temp
```

Plot only header tanks 



Select only tanks, not header tanks
```{r}
tank_data <- rbind(amb_tank1_A, amb_tank1_B, amb_tank2_A, amb_tank2_B, high_tank1_A, high_tank1_B, high_tank2_A, high_tank2_B)

colnames(tank_data) <- c("Date.Time", "Temp", "Light", "Treatment", "Tank")
tank_data$Date.Time <- parse_date_time(tank_data$Date.Time, "mdyHMS", tz = "HST")
```

Filter data after 7/12 and before 7/18 - when experiment began and ended, respectively 
```{r}
filt_tank_data <- tank_data %>% 
  filter(Date.Time > "2022-07-12 12:00:00") %>%
  filter(Date.Time < "2022-07-18 20:00:00")
```

Plot only tank data
```{r}
temp <- filt_tank_data %>% ggplot(aes(x=Date.Time, y=Temp)) +
  geom_line(aes(color = Tank), size = 1) +
  ylab("Temperature °C") + 
  #geom_vline(xintercept = as.POSIXct(as.Date(c("2022-07-05 18:00:00")))) +
  #geom_vline(xintercept = as.POSIXct(as.Date(c("2022-07-08 18:00:00")))) +
  scale_color_manual(values=c("lightblue", "lightblue", "lightblue", "lightblue", "pink", "pink", "pink", "pink"))
temp
```

One of the high tanks has a large temp decreaese on July 18 because I took it out of the tank and forgot to put it back in? Check notebook

Calculate tank averages
```{r}
# Function to calculate standard error
std_error <- function(x) {
  sd(x, na.rm = TRUE) / sqrt(length(na.omit(x)))
}

# Calculate the average and standard error for each time point and treatment
avg_tank_data <- filt_tank_data %>%
  group_by(Date.Time, Treatment) %>%
  summarise(
    Avg_Temp = mean(Temp, na.rm = TRUE),
    SE_Temp = std_error(Temp),
    Avg_Light = mean(Light, na.rm = TRUE),
    SE_Light = std_error(Light)) %>%
  filter(SE_Temp < 0.5)
```

Plot only tank data for experimental period 
```{r}
avg_temp <- avg_tank_data %>%
  ggplot(aes(x = Date.Time, y = Avg_Temp, color = Treatment)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = Avg_Temp - SE_Temp, ymax = Avg_Temp + SE_Temp, fill = Treatment), alpha = 0.2) +
  ylab("Temperature (°C)") +
  scale_color_manual(values = c("blue", "red")) +
  scale_fill_manual(values = c("blue", "red"))+
  theme_light()
avg_temp
```

## Plot light data
```{r}
light <- filt_tank_data %>% ggplot(aes(x=Date.Time, y=Light)) +
  geom_line(aes(color = Tank), size = 1) +
  ylab("Light (lux)") + 
  scale_color_manual(values=c("darkblue", "lightblue", "lightblue", "lightblue", "lightblue", "darkred", "pink", "pink", "pink", "pink"))
light

## Remove light values above 20,000 lux
light_less <- filt_data[filt_data$Light < 20000, ]
less <- light_less %>% ggplot(aes(x=Date.Time, y=Light)) +
  geom_line(aes(color = Tank), size = 1) +
  ylab("Light (lux)") + 
  scale_color_manual(values=c("darkblue", "lightblue", "lightblue", "lightblue", "lightblue", "darkred", "pink", "pink", "pink", "pink"))
less
```









