---
title: "logger data"
author: "jillashey"
date: '2022-07-11'
output: html_document
---

This script plots Hobo temperature and light data from an adult acute thermal stress experiment at HIMB 2022. 

## Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(tidyverse)
library(emmeans)
library(gridExtra)
```

## Read data in 
```{r}
## Ambient
# Ambient Header
amb_header <- read.csv("data/temperature/20220719/Amb_Header_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
amb_header$Treatment <- "Ambient"
amb_header$Tank <- "Ambient-Header"

# Amb Tank 1 A
amb_tank1_A <- read.csv("data/temperature/20220719/Amb1_Tank_A_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
amb_tank1_A$Treatment <- "Ambient"
amb_tank1_A$Tank <- "Ambient1-Tank-A"

# Amb Tank 1 B
amb_tank1_B <- read.csv("data/temperature/20220719/Amb1_Tank_B_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
amb_tank1_B$Treatment <- "Ambient"
amb_tank1_B$Tank <- "Ambient1-Tank-B"

# Amb Tank 2 A
amb_tank2_A <- read.csv("data/temperature/20220719/Amb2_Tank_A_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
amb_tank2_A$Treatment <- "Ambient"
amb_tank2_A$Tank <- "Ambient2-Tank-A"

# Amb Tank 2 B
amb_tank2_B <- read.csv("data/temperature/20220719/Amb2_Tank_B_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
amb_tank2_B$Treatment <- "Ambient"
amb_tank2_B$Tank <- "Ambient2-Tank-B"



## High
# High Header
high_header <- read.csv("data/temperature/20220719/High_Header_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
high_header$Treatment <- "High"
high_header$Tank <- "High-Header"

# High Tank 1 A
high_tank1_A <- read.csv("data/temperature/20220719/High1_Tank_A_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
high_tank1_A$Treatment <- "High"
high_tank1_A$Tank <- "High1-Tank-A"

# High Tank 1 B
high_tank1_B <- read.csv("data/temperature/20220719/High1_Tank_B_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
high_tank1_B$Treatment <- "High"
high_tank1_B$Tank <- "High1-Tank-B"

# High Tank 2 A
high_tank2_A <- read.csv("data/temperature/20220719/High2_Tank_A_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
high_tank2_A$Treatment <- "High"
high_tank2_A$Tank <- "High2-Tank-A"

# High Tank 2 B
high_tank2_B <- read.csv("data/temperature/20220719/High2_Tank_B_20220719.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
high_tank2_B$Treatment <- "High"
high_tank2_B$Tank <- "High2-Tank-B"
```

## Bind dataframes together and parse data & time
```{r}
data <- rbind(amb_header, amb_tank1_A, amb_tank1_B, amb_tank2_A, amb_tank2_B,
                high_header, high_tank1_A, high_tank1_B, high_tank2_A, high_tank2_B)

colnames(data) <- c("Date.Time", "Temp", "Light", "Treatment", "Tank")
data$Date.Time <- parse_date_time(data$Date.Time, "mdyHMS", tz = "HST")
```

## Subset data after 7/8/22 - when temperature ramp began
```{r}
filt_data <- data %>% filter(Date.Time > "2022-07-08 12:00:00")
```

## Plot temperature data
```{r}
temp <- filt_data %>% ggplot(aes(x=Date.Time, y=Temp)) +
  geom_line(aes(color = Tank), size = 1) +
  ylab("Temperature °C") + 
  #geom_vline(xintercept = as.POSIXct(as.Date(c("2022-07-05 18:00:00")))) +
  #geom_vline(xintercept = as.POSIXct(as.Date(c("2022-07-08 18:00:00")))) +
  scale_color_manual(values=c("darkblue", "lightblue", "lightblue", "lightblue", "lightblue", "darkred", "pink", "pink", "pink", "pink"))
temp

# Save plot
ggsave("output/temperature/Temperature.Treatment.pdf", plot = last_plot(), width = 8, height = 4)
```

## Plot light data
```{r}
light <- filt_data %>% ggplot(aes(x=Date.Time, y=Light)) +
  geom_line(aes(color = Tank), size = 1) +
  ylab("Light (lux)") + 
  scale_color_manual(values=c("darkblue", "lightblue", "lightblue", "lightblue", "lightblue", "darkred", "pink", "pink", "pink", "pink"))
light
ggsave("output/temperature/Light.pdf", plot = last_plot(), width = 8, height = 4)


## Remove light values above 20,000 lux
light_less <- filt_data[filt_data$Light < 20000, ]
less <- light_less %>% ggplot(aes(x=Date.Time, y=Light)) +
  geom_line(aes(color = Tank), size = 1) +
  ylab("Light (lux)") + 
  scale_color_manual(values=c("darkblue", "lightblue", "lightblue", "lightblue", "lightblue", "darkred", "pink", "pink", "pink", "pink"))
less
```


# Plot by treatment

## Separate into treatment dataframes 
```{r}
amb <- filt_data %>% filter(Treatment == "Ambient")
high <- filt_data %>% filter(Treatment == "High")
```

## Plot by temperature 
```{r}
## Ambient 
amb_temp <- amb %>% ggplot(aes(x=Date.Time, y=Temp)) +
  geom_line(aes(color = Tank), size = 1) +
  ylab("Temperature °C") + 
  scale_color_manual(values=c("darkblue", "lightblue", "lightblue", "lightblue", "lightblue"))
amb_temp
ggsave("output/temperature/Ambient.Treatment.pdf", plot = last_plot(), width = 8, height = 4)



## High
high_temp <- high %>% ggplot(aes(x=Date.Time, y=Temp)) +
  geom_line(aes(color = Tank), size = 1) +
  ylab("Temperature °C") + 
  scale_color_manual(values=c("darkred", "pink", "pink", "pink", "pink"))
high_temp
ggsave("output/temperature/High.Treatment.pdf", plot = last_plot(), width = 8, height = 4)

```

## Looking at High Tank 1 & High Tank 2
## Separate into treatment dataframes 
```{r}
## High1 tank
high1 <- high %>% filter(Tank == "High1-Tank-A" | Tank == "High1-Tank-B")
high1_temp <- high1 %>% ggplot(aes(x=Date.Time, y=Temp)) +
  geom_line(aes(color = Tank), size = 1) +
  ylab("Temperature °C") + 
  scale_color_manual(values=c("purple", "pink"))
high1_temp


## High2 tank
high2 <- high %>% filter(Tank == "High2-Tank-A" | Tank == "High2-Tank-B")
high2_temp <- high2 %>% ggplot(aes(x=Date.Time, y=Temp)) +
  geom_line(aes(color = Tank), size = 1) +
  ylab("Temperature °C") + 
  scale_color_manual(values=c("purple", "pink"))
high2_temp
```





