---
title: "prelim_hawaii_temps"
author: "jillashey"
date: '2022-06-12'
output: pdf_document
---

## Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lubridate)
library(tidyverse)
library(emmeans)
library(gridExtra)
```

################## Below is prelim data from 6/12/22 ################## 

This script shows some *preliminary* hobo logger data from 6/11/22 - 6/17/22 HST. This information will be used to determine treatment temperatures for our experiments in Hawaii 2022

Squaricals 1-6: High
Squaricals 7-12: Ambient

## Read data in and parse date & time
```{r}
# High Header
high_header <- read.csv("data/temperature/20220705/High_Header_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(high_header) <- c("Date", "Temperature_High_Header", "Light-High_Header")
high_header$Date <- parse_date_time(high_header$Date, "mdyHMS", tz = "HST")
high_header$Treatment <- "High"

# High Tank 1
high_tank1 <- read.csv("data/temperature/20220705/High1_Tank_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(high_tank1) <- c("Date", "Temperature_High_Tank1", "Light-High_Tank1")
high_tank1$Date <- parse_date_time(high_tank1$Date, "mdyHMS", tz = "HST")
high_tank1$Treatment <- "High"

# High Tank 2
high_tank2 <- read.csv("data/temperature/20220705/High2_Tank_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(high_tank2) <- c("Date", "Temperature_High_Tank2", "Light-High_Tank2")
high_tank2$Date <- parse_date_time(high_tank2$Date, "mdyHMS", tz = "HST")
high_tank2$Treatment <- "High"

# High Squarical 1
high_sq1 <- read.csv("data/temperature/20220705/Squarical1_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(high_sq1) <- c("Date", "Temperature_High_Sq1", "Light-High_Sq1")
high_sq1$Date <- parse_date_time(high_sq1$Date, "mdyHMS", tz = "HST")
high_sq1$Treatment <- "High"

# High Squarical 2
high_sq2 <- read.csv("data/temperature/20220705/Squarical2_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(high_sq2) <- c("Date", "Temperature_High_Sq2", "Light-High_Sq2")
high_sq2$Date <- parse_date_time(high_sq2$Date, "mdyHMS", tz = "HST")
high_sq2$Treatment <- "High"

# High Squarical 3
################################################### No logger data after 6/19/22
high_sq3 <- read.csv("data/temperature/20220619/Squarical3_20220619.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(high_sq3) <- c("Date", "Temperature_High_Sq3", "Light-High_Sq3")
high_sq3$Date <- parse_date_time(high_sq3$Date, "mdyHMS", tz = "HST")
high_sq3$Treatment <- "High"

# High Squarical 4
################################################### No logger data after 6/19/22
high_sq4 <- read.csv("data/temperature/20220619/Squarical4_20220619.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(high_sq4) <- c("Date", "Temperature_High_Sq4", "Light-High_Sq4")
high_sq4$Date <- parse_date_time(high_sq4$Date, "mdyHMS", tz = "HST")
high_sq4$Treatment <- "High"

# High Squarical 5
high_sq5 <- read.csv("data/temperature/20220705/Squarical5_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(high_sq5) <- c("Date", "Temperature_High_Sq5", "Light-High_Sq5")
high_sq5$Date <- parse_date_time(high_sq5$Date, "mdyHMS", tz = "HST")
high_sq5$Treatment <- "High"

# High Squarical 6
high_sq6 <- read.csv("data/temperature/20220705/Squarical6_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(high_sq6) <- c("Date", "Temperature_High_Sq6", "Light-High_Sq6")
high_sq6$Date <- parse_date_time(high_sq6$Date, "mdyHMS", tz = "HST")
high_sq6$Treatment <- "High"


## Ambient
# Ambient Header
amb_header <- read.csv("data/temperature/20220705/Amb_Header_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(amb_header) <- c("Date", "Temperature_Amb_Header", "Light-Amb_Header")
amb_header$Date <- parse_date_time(amb_header$Date, "mdyHMS", tz = "HST")
amb_header$Treatment <- "Ambient"

# Amb Tank 1
amb_tank1 <- read.csv("data/temperature/20220705/Amb1_Tank_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(amb_tank1) <- c("Date", "Temperature_Amb_Tank1", "Light-Amb_Tank1")
amb_tank1$Date <- parse_date_time(amb_tank1$Date, "mdyHMS", tz = "HST")
amb_tank1$Treatment <- "Ambient"

# Amb Tank 2
amb_tank2 <- read.csv("data/temperature/20220705/Amb2_Tank_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(amb_tank2) <- c("Date", "Temperature_Amb_Tank2", "Light-Amb_Tank2")
amb_tank2$Date <- parse_date_time(amb_tank2$Date, "mdyHMS", tz = "HST")
amb_tank2$Treatment <- "Ambient"

# Ambient Squarical 7
################################################### No logger data after 6/19/22
amb_sq7 <- read.csv("data/temperature/20220619/Squarical7_20220619.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(amb_sq7) <- c("Date", "Temperature_Amb_Sq7", "Light-Amb_Sq7")
amb_sq7$Date <- parse_date_time(amb_sq7$Date, "mdyHMS", tz = "HST")
amb_sq7$Treatment <- "Ambient"

# Ambient Squarical 8
amb_sq8 <- read.csv("data/temperature/20220705/Squarical8_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(amb_sq8) <- c("Date", "Temperature_Amb_Sq8", "Light-Amb_Sq8")
amb_sq8$Date <- parse_date_time(amb_sq8$Date, "mdyHMS", tz = "HST")
amb_sq8$Treatment <- "Ambient"

# Ambient Squarical 9
amb_sq9 <- read.csv("data/temperature/20220705/Squarical9_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(amb_sq9) <- c("Date", "Temperature_Amb_Sq9", "Light-Amv_Sq9")
amb_sq9$Date <- parse_date_time(amb_sq9$Date, "mdyHMS", tz = "HST")
amb_sq9$Treatment <- "Ambient"

# Ambient Squarical 10
################################################### No logger data after 6/19/22
amb_sq10 <- read.csv("data/temperature/20220619/Squarical10_20220619.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(amb_sq10) <- c("Date", "Temperature_Amb_Sq10", "Light-Amb_Sq10")
amb_sq10$Date <- parse_date_time(amb_sq10$Date, "mdyHMS", tz = "HST")
amb_sq10$Treatment <- "Ambient"

# Ambient Squarical 11
amb_sq11 <- read.csv("data/temperature/20220705/Squarical11_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(amb_sq11) <- c("Date", "Temperature_Amb_Sq11", "Light-Amb_Sq11")
amb_sq11$Date <- parse_date_time(amb_sq11$Date, "mdyHMS", tz = "HST")
amb_sq11$Treatment <- "Ambient"

# Ambient Squarical 12
amb_sq12 <- read.csv("data/temperature/20220705/Squarical12_20220705.csv", sep=",", header=T, na.strings = "NA")[ ,2:4]
colnames(amb_sq12) <- c("Date", "Temperature_Amb_Sq12", "Light-Amb_Sq12")
amb_sq12$Date <- parse_date_time(amb_sq12$Date, "mdyHMS", tz = "HST")
amb_sq12$Treatment <- "Ambient"
```

## Join all dataframes 
```{r}
# Put dfs into a list 
df_list <- list(amb_header, amb_tank1, amb_tank2, amb_sq7, amb_sq8, amb_sq9, amb_sq10, amb_sq11, amb_sq12,
                high_header, high_tank1, high_tank2, high_sq1, high_sq2, high_sq3, high_sq4, high_sq5, high_sq6)

# Merge dfs together by date 
data <- df_list %>% reduce(full_join, by='Date')
```

## Convert to long 
```{r}
data <- data %>% select(Date, Temperature_Amb_Header, Temperature_Amb_Tank1, Temperature_Amb_Tank2, Temperature_Amb_Sq7, Temperature_Amb_Sq8, Temperature_Amb_Sq9, Temperature_Amb_Sq10, Temperature_Amb_Sq11, Temperature_Amb_Sq12, Temperature_High_Header, Temperature_High_Tank1, Temperature_High_Tank2, Temperature_High_Sq1, Temperature_High_Sq2, Temperature_High_Sq3, Temperature_High_Sq4, Temperature_High_Sq5, Temperature_High_Sq6) %>% 
  pivot_longer(cols = Temperature_Amb_Header:Temperature_High_Sq6, names_to = "Location") %>%
  na.omit(data)
```

## Add treatment to dataframe
```{r}
data <- data %>% 
  mutate(Treatment = case_when(
    Location == "Temperature_Amb_Header" ~ "Ambient",
    Location == "Temperature_Amb_Tank1" ~ "Ambient",
    Location == "Temperature_Amb_Tank2" ~ "Ambient",
    Location == "Temperature_Amb_Sq7" ~ "Ambient",
    Location == "Temperature_Amb_Sq8" ~ "Ambient",
    Location == "Temperature_Amb_Sq9" ~ "Ambient",
    Location == "Temperature_Amb_Sq10" ~ "Ambient",
    Location == "Temperature_Amb_Sq11" ~ "Ambient",
    Location == "Temperature_Amb_Sq12" ~ "Ambient",
    Location == "Temperature_High_Header" ~ "High",
    Location == "Temperature_High_Tank1" ~ "High",
    Location == "Temperature_High_Tank2" ~ "High",
    Location == "Temperature_High_Sq1" ~ "High",
    Location == "Temperature_High_Sq2" ~ "High",
    Location == "Temperature_High_Sq3" ~ "High",
    Location == "Temperature_High_Sq4" ~ "High",
    Location == "Temperature_High_Sq5" ~ "High",
    Location == "Temperature_High_Sq6" ~ "High"
  ))

# try to use 'contains' instead of 'case_when'
```

## Plot temperature data
```{r}
plot <- ggplot(data, aes(x=Date, y=value)) +
  geom_line(aes(color = Location), size = 1)+
  ylab("Temperature °C") +
  scale_color_manual(values=c("blue","blue","blue", "blue", "blue", "blue", "blue", "blue", "blue", "red", "red", "red", "red", "red", "red", "red", "red", "red"))
plot

ggsave("output/temperature/Prelim.Temp.Treatments.pdf", plot = last_plot(), width = 8, height = 4)
```

## Subset and plot ambient temperature data
```{r}
amb_data <- data %>% filter(Treatment == "Ambient")

amb_plot <- ggplot(amb_data, aes(x=Date, y=value)) +
  geom_line(aes(color = Location), size = 1) +
  ylab("Temperature °C") +
  scale_color_manual(values=c("darkblue","blue","blue", "blue", "blue", "blue", "blue", "lightblue", "lightblue"))
amb_plot

ggsave("output/temperature/Prelim.Ambient.Treatments.pdf", plot = last_plot(), width = 8, height = 4)
```

## Subset and plot high temperature data
```{r}
high_data <- data %>% filter(Treatment == "High") 

high_data <- ggplot(high_data, aes(x=Date, y=value)) +
  geom_line(aes(color = Location), size = 1) +
  ylab("Temperature °C") +
  scale_color_manual(values=c("darkred","red","red", "red", "red", "red", "red", "pink", "pink"))
high_data

ggsave("output/temperature/Prelim.High.Treatments.pdf", plot = last_plot(), width = 8, height = 4)
```


plot to see where how fast the high treatments ramp 
```{r}
test <- data %>% filter(Date < "2022-06-12 11:00:00", Date > "2022-06-12 09:40:00")

plot <- ggplot(test, aes(x=Date, y=value)) +
  geom_line(aes(color = Location), size = 1) +
  ylab("Temperature °C") +
  scale_color_manual(values=c("blue","blue","blue", "blue", "blue", "blue", "blue", "blue", "blue", "red", "red", "red", "red", "red", "red", "red", "red", "red"))
plot
```

Looking at high treatment during this window of time 
```{r}
high_test <- test %>% filter(Treatment == "High") 

plot2 <- ggplot(high_test, aes(x=Date, y=value)) +
  geom_line(aes(color = Location), size = 1) +
  ylab("Temperature °C") +
  scale_color_manual(values=c("darkred","red","red", "red", "red", "red", "red", "pink", "pink"))
plot2
```





